Anomaly_inspection

### 2021-01-16 anomaly.Rmd
Edit some codes and add boxplot to show extreme values

#calculate the variance of the lm model's residual 
#sort it from the highest to the lowest
wages_lm_var <- wages_res %>%
  group_by(id) %>%
  summarise(var = var(mean_hourly_wage,
                      na.rm = TRUE)) %>%
  arrange(desc(var)) 
```

@@

@@

The volatility in wages, could be seen in the id with high and low variance. For example, in id 951 (high variance) and 7611 (small variance).

>>>>

#calculate the variance of the lm model's residual 
#sort it from the highest to the lowest
wages_lm_var <- wages_res %>%
  group_by(id) %>%
  summarise(var = var(resid,
                      na.rm = TRUE)) %>%
  arrange(desc(var)) 
```

@@

```{r}
wages %>%
  filter(id == 11974)
```

@@

```{r}
wages %>%
  filter(year == 1984)
```

```{r}
ggplot(wages) +
  geom_boxplot(aes(x = mean_hourly_wage)) +
  facet_wrap(~year)
```
